Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-08-11 Master Thesis/synopsis.tex
Fixing comma mistakes

\begin{lemma}\label{2.2-pre}
Let $v,w\in\operatorname{Spv}(K)$. We have:
\[\mathcal{O}_w\subset\mathcal{O}_v \iff w\in\overline{\{v\}} \]
Thus $v$ is a closed point if and only if it has no non-trivial specializations. For a fixed $v\in \operatorname{Spv}(K)$ there is a canonical bijection: 
\begin{align*}
\{ w\in\operatorname{Spv}(K)\mid \mathcal{O}_w\subset\mathcal{O}_v \} &\longrightarrow \operatorname{Spv}k(v)\\ 
w&\longmapsto w\mod v
\end{align*}
Therefore $v$ is a closed point if and only if $k(v)$ only admits the trivial valuation, i.e. $k(v)$ has characteristic $p>0$ and is algebraic over $\mathbb{F}_p$. In other words, if $|\operatorname{Spv}(K)|$ denotes the set of all closed points in $\operatorname{Spv}(K)$, we have:
\[ |\operatorname{Spv}(K)|=\{v\in\operatorname{Spv}(K)\mid \dim k(v)=0\} \]
If $w\in\operatorname{Spv}_\text{rd}^{(i)}(K)$ for some $i\geq 1$ then there exists a unique $v(w)\in\operatorname{Spv}_\text{rd}^{(i-1)}(K)$ such that $\mathcal{O}_w\subset\mathcal{O}_{v(w)}$. $w$ is henselian if and only if $v(w)$ and $w\mod v(w)$ are henselian.
\end{lemma}

@@

Let $A\subset \operatorname{Spv}(K)$ be a closed set, $S\subset K$ finite, and let $U_S\cap A\neq\varnothing$. Assume there exist a point $v\in U_S\cap A$ which is not closed. Let $\overline{S}$ be the image of $S\subset \mathcal{O}_v$ in $k(v)$. If $\operatorname{char}k(v)=0$, then $R=\mathbb{Z}[\overline{S}]\subset k(v)$ is a subring that is not a field, since $\overline{S}$ is finite. If $\operatorname{char} k(v)=p>0$, $k(v)/\mathbb{F}_p$ is not an algebraic extension, thus we can find an element $T\in k(v)$ which is transcendental over $\mathbb{F}_p$. In this case, $R=\mathbb{F}_p[T, \overline{S}]\subset k(v)$ is a subring that is not a field. In both cases, \cite{ZS60} VI, §4 Corollary 1 to Lemma guarantees the existence of a non-trivial valuation $\widetilde{v_1}\in\operatorname{Spv}k(v)$ with $\overline{S}\subset R\subset \mathcal{O}_{\widetilde{v_1}}$. By Lemma \ref{2.2-pre}, $\widetilde{v_1}$ corresponds to a valuation $v_1\in\operatorname{Spv}(K)$ with $S\subset \mathcal{O}_{v_1}\subsetneq \mathcal{O}_v$, i.e. $v_1\in \overline{\{v\}}\cap U_S$ and $\operatorname{rank}(v_1)>\operatorname{rank}(v)$. Repeating this process for $v_1$ and so on, we get a specialization chain of valuations in $U_S$:
\[\mathcal{O}_v\supsetneq \mathcal{O}_{v_1}\supsetneq\cdots \supsetneq\mathcal{O}_{v_n} \]
Since $K$ is assumed to be finite dimensional, Lemma \ref{rank-dimension-inequality} assures that this sequence ends with a closed point $v_n\in \overline{\{v\}}\cap U_S\subset A\cap U_S$.

@@

\begin{proof}
Assume that $K$ is not algebraically closed. $w_1$ and $w_2$ can't be trivial, for otherwise $\dim k(w_i)=\dim (K)\neq 0$. By the Theorem of F.K. Schmidt \ref{theorem-fkschmidt}, we can see that $w_1,w_2$ are dependent. Since two different valuations of rank $1$ are independent, at least one of $w_1$ and $w_2$ is of rank $2$. Now, assume that $w_1$ is, say, of rank $1$ and $w_2$ is of rank $2$. Since they are dependent, it follows $v(w_2) = w_1$ and $w_1$ has a non-trivial specialization, a contradiction to $w_1\in |\operatorname{Spv}(K)|$.

Thus $w_1,w_2$ are both of rank $2$ and by Lemma \ref{rank-dimension-inequality} we can see that $w_1,w_2\in\operatorname{Spv}_\text{rd}^{(2)}(K)$. Set $v_i=v(w_i)\in\operatorname{Spv}^{(1)}_\text{d}(K)$. By Lemma \ref{2.2-pre} $K$ is henselian with respect to both $v_1$ and $v_2$. Again, by the Theorem of F.K. Schmidt \ref{theorem-fkschmidt}, we get $v_1 = v_2$. Furthermore $k(v_1) = k(v_2)$ is henselian with respect to two different valuations of rank $1$, namely $w_1\mod v_1$ and $w_2\mod v_1$, making $k(v_1)$ separably closed.

For the second assertion, let $K$ be not algebraically closed and $v=v(w_1)=v(w_2)\in\operatorname{Spv}_\text{d}^{(1)}(K)$. The restriction $v|$ of $v$ on $k=\mathbb{Q}(T)\subset K$ is a discrete valuation. Choose a henselization $k_{v|}$ of $k$ such that $k_{v|}\subset K$ and consider the absolute inertia field $k_{v|}^\text{t}$ of $k_{v|}$. Since $k(v)$ is separably closed, we have $k_{v|}^\text{t}\subset K$, i.e. $G_K\subset G_{k_{v|}^\text{t}}$. Since $v|\in \operatorname{Spv} ({k_{v|}^\text{t}})$ is discrete and henselian, \cite{Ka79} §5, Theorem 1 shows $\operatorname{cd}\big(G_{k_{v|}^\text{t}}\big)\leq 2$. In particular, $\operatorname{cd}(G_K)\leq 2$.
\end{proof}

@@

\begin{proof}
Let $T$ be the absolute inertia group of $K$ and $V\lhd T$ its absolute ramification group. By Theorem \ref{theorem-sylowgroups-inertiagroup}, $V$ is the $p$-Sylow group of $T$ and the $\ell$-Sylow group of $T/V$ is isomorphic to $\mathbb{Z}_\ell$. Therefore, by \cite{Se64} Ch. I, §3 Proposition 15:
\[ \operatorname{cd}_\ell(T)\leq \operatorname{cd}_\ell(V) + \operatorname{cd}_\ell(\mathbb{Z}_\ell) = 1 \]
By Theorem \ref{theorem-absoluteinertia}, we have an isomorphism $G_K/T\cong G_k$. Furthermore, we have $\operatorname{cd}_\ell(G_K/T)=\operatorname{cd}_\ell(k)\leq 2$ by requirement,
thus the following Hochschild-Serre spectral sequence degenerates on $E_2$:
\[E_2^{i,j}=\mathrm{H}^i(G_K/T, \mathrm{H}^j(T, \mathbb{Z}/\ell\mathbb{Z}(2)))\Longrightarrow\mathrm{H}^{i+j}(G_K, \mathbb{Z}/\ell\mathbb{Z}(2))\]
It yields an isomorphism $\mathrm{H}^2(k, \mathrm{H}^1(T, \mathbb{Z}/\ell\mathbb{Z}(2)))\cong \mathrm{H}^3(K, \mathbb{Z}/\ell\mathbb{Z}(2))$. Since $\mu_{\ell}$ is contained in the absolute inertia field of $K$, $T$ acts trivially on $\mu_{\ell}$, hence:
\[ \mathrm{H}^1(T, \mathbb{Z}/\ell\mathbb{Z}(2)) \cong \mathrm{H}^1(T, \mu_{\ell}) \cong \operatorname{Hom}_\text{cont.}(T, \mu_{\ell}) \cong \operatorname{Hom}_\text{cont.}(T/V, \mu_{\ell}) \]
By Theorem \ref{theorem-sylowgroups-inertiagroup}, $T/V$ is the free pro-$\mathcal{C}$ group of rank $1$, where $\mathcal{C}$ is the class of all finite groups with order prime to $p$. Therefore, $\operatorname{Hom}_\text{cont.}(T/V, \mu_{\ell})\cong \mu_{\ell}$. The rest follows from Proposition \ref{prop:kummer-theory}.
\end{proof}

The following lemma is the key result in proving Theorem \ref{thm:main-result}. First, we use K. Kato's two-dimensional local-global principle to show the assertion for finitely generated $K$. Then, we'll use a quasi-compactness argument to see that we can drop the assumption that $K$ is finitely generated.

@@

\begin{proof}
Let $L=K(\mu_{\ell},\sqrt{-1})/K$. Consider the restriction and corestriction maps:
\[ \begin{tikzcd}
\mathrm{H}^3(K,\mathbb{Z}/\ell\mathbb{Z}) \ar[r, "\operatorname{res}"] & \mathrm{H}^3(L,\mathbb{Z}/\ell\mathbb{Z})\ar[r, "\operatorname{cor}"]& \mathrm{H}^3(K,\mathbb{Z}/\ell\mathbb{Z}) 
\end{tikzcd} \]
We have $\operatorname{cor}\circ\operatorname{res} = [L:K]$. Since $[L:K]$ is coprime to $\ell$, we see that $\operatorname{res}$ is injective. Thus we can assume that $K=L$, i.e. $\mu_{\ell}\subset K$ and $K$ is not formally real. Now we can replace $\mathbb{Z}/\ell\mathbb{Z}$ by $\mathbb{Z}/\ell\mathbb{Z}(2) = \mu_\ell^{\otimes 2}$ and let us write $\mathrm{H}^3(L) = \mathrm{H}^3(L, \mathbb{Z}/\ell\mathbb{Z}(2))$.

@@

Let $v$ be a discrete valuation of $K$ with residue field $k=k(v)$. Consider the following map induced by the restriction maps: 
\[ \phi: \mathrm{H}^3(K_v) \longrightarrow \prod_w\mathrm{H}^3(K_w) \]
where $w$ ranges over all rank-$2$ valuations with $v(w) = v$. By Lemma \ref{rank-dimension-inequality}, we have $\dim(k) = 1$, thus $k$ is a global field of characteristic $0$, hence a number field. \cite{Se64} Ch. II, §4 Prop. 13 shows $\operatorname{cd}_\ell(k)\leq 2$. With Lemma \ref{2.4-pre}, $\phi$ can be identified with
\[ {}_\ell\operatorname{Br}(k) \longrightarrow \prod_{\widetilde{w}\in\operatorname{Spv}^{(1)}(k)} {}_\ell\operatorname{Br}(k_{\widetilde{w}}) \]
which is injective by the classical Hasse principle. Furthermore, its image is contained in $\bigoplus {}_\ell\operatorname{Br}(k_{\widetilde{w}})$. Combining these maps yields the following injection:
\[\Phi: \mathrm{H}^3(K)\longrightarrow \bigoplus_{x\in\mathfrak{X}_1}\  \bigoplus_{\substack{w\in\operatorname{Spv}_\text{rd}^{(2)}(K) \\ v(w) = v_x}} \mathrm{H}^3(K_w) \]
The direct sum ranges over a subset of $|\operatorname{Spv}(K)|$, thus this concludes the proof. 
\end{proof}

@@

\begin{proof}
We adopt the notation from the previous proof. First, we shall prove that the following map is injective for every model $\mathfrak{X}$ of $K$:
\[ f: \mathrm{H}^3(K) \longrightarrow \prod_{y\in\mathfrak{X}_0}\mathrm{H}^3(K_y) \]
For $x\in\mathfrak{X}$ let $\mathcal{O}_x$ be a henselization of $\mathcal{O}_{\mathfrak{X}, x}$ and $K_x$ its quotient field. For $y\in\mathfrak{X}_0$ set $P_y=\operatorname{Spec}(\mathcal{O}_y)_1$. For $z\in P_y$ let $\mathcal{O}_z$ be a henselization of $\mathcal{O}_y$ at $z$ and $K_z$ its quotient field. For $y\in\mathfrak{X}_0$ and $x\in\mathfrak{X}_1$ let $P_{x,y}$ be the subset of $P_y$ consisting of all $z\in P_y$ which are mapped to $x$ under $\operatorname{Spec}(\mathcal{O}_y)\to\mathfrak{X}$. Consider the following commutative diagram:
\[ \begin{tikzcd}
\mathrm{H}^3(K)\ar[r, "\varphi"]\ar[d, "f"'] & \displaystyle\prod_{x\in\mathfrak{X}_1}\mathrm{H}^3(K_x)\ar[d, "\psi"]\\
\displaystyle\prod_{y\in\mathfrak{X}_0}\mathrm{H}^3(K_y) \ar[r, "g"']& \displaystyle\prod_{\substack{x\in\mathfrak{X}_1 \\ y\in\mathfrak{X}_0}}\prod_{z\in P_{x,y}}\mathrm{H}^3(K_z)
\end{tikzcd} \]
According to \cite{Sa87} Theorem 5.3, $g$ is injective. Now, $\psi\circ\varphi$ can be identified with the injective map $\Phi$ from the proof of the previous Lemma. Thus its image is contained in $\bigoplus\mathrm{H}^3(K_w)$. Therefore, $f$ is injective as well and its image is contained in $\bigoplus\mathrm{H}^3(K_y)$. Therefore, the set
\[ A_\mathfrak{X} = \{ y\in\mathfrak{X}_0\mid \operatorname{res}_{K_y/K}(\alpha)\neq 0 \} \]
is finite, thus closed in $\mathfrak{X}$. Now Lemma \ref{2.3} (i) yields
\[ \operatorname{supp}(\alpha) = \bigcap_{\mathfrak{X}\in \mathfrak{M}(K)} \pi_\mathfrak{X}^{-1}(A_\mathfrak{X}) \]
and the right-hand side is closed in $\operatorname{Spv}(K)$.
\end{proof}

@@

Let $w\in |\operatorname{Spv}(K)|$. We denote the restriction of $w$ to $K_i$ with $w$ as well. Since $\mathrm{H}^3(K_w) = \varinjlim_I \mathrm{H}^3((K_i)_w)$ there exists an $i = i(w)\in I$ such that $\operatorname{res}_{(K_i)_w/K}(g) = 0$. By Lemma \ref{2.4-closedset} there is an open neighborhood $U_{i(w)}\subset |\operatorname{Spv}(K_i)|$ of $w$ such that $\operatorname{res}_{(K_i)_v/K}(g)=0$ for all $v\in U_{i(w)}$. For $K_i\subset K_j\subset K$ let
\[ \varphi_i: |\operatorname{Spv}(K)| \to |\operatorname{Spv}(K_i)| \]
\[ \varphi_{ij}: |\operatorname{Spv}(K_j)|\to |\operatorname{Spv}(K_i)| \]
be the restriction maps. They are continuous. Since $|\operatorname{Spv}(K)|$ is quasi-compact by Lemma \ref{spv-topology} we can find a finite set $S\subset |\operatorname{Spv}(K)|$ such that:
\[ \bigcup_{w\in S}\varphi^{-1}_{i(w)}(U_{i(w)}) = |\operatorname{Spv}(K)| \]
Let $j\in I$ such that $K_j$ is the composite of the fields $K_{i(w)},\ w\in S$. Then we have:
\[ \bigcup_{w\in S}\varphi^{-1}_{i(w)j}(U_{i(w)}) = |\operatorname{Spv}(K_j)| \]
Let $v\in |\operatorname{Spv}(K_j)|$ and let $i = i(w),\ w\in S$ such that $v\in\varphi_{ij}^{-1}(U_{i(w)})$. We have:
\[ \operatorname{res}_{(K_j)_v/K_j}(\operatorname{res}_{K_j/K_0}(\beta)) = \operatorname{res}_{(K_j)_v/(K_i)_v}(\operatorname{res}_{(K_i)_v/K_0}(\beta)) = 0 \]
Since $K_j$ is finitely generated we obtain $\operatorname{res}_{K_j/K_0}(\beta) = 0$ with Lemma \ref{2.4-finitelygenerated}, thus $\alpha = \operatorname{res}_{K/K_0}(\beta) = 0$.
\end{proof}

@@

By Proposition \ref{2.5}, $E_0/E$, and also $E'_0/E'$, satisfy the condition of Proposition \ref{2.6} for both $\ell_1$ and $\ell_2$. Thus there exists a unique henselian valuation $w'_{E'}\in|\operatorname{Spv}(E')|$. Now $E'$ contains a henselization $K'_{w'}$ with respect to $w' = w'_{E'}|_{K'}$. By applying the same argument to $\sigma^{-1}$ we find that $E' = K'_{w'}$.

@@

Let $w_1,w_2 \in\operatorname{Spv}_\text{d}^{(2)}(K)$ be two different valuations. Then the following statements are equivalent:
\begin{enumerate}[(i)]
\item The composite $K_{w_1}K_{w_2}$ is not algebraically closed.
\item $w_1,w_2\in\operatorname{Spv}_\text{rd}^{(2)}(K)$ and $v(w_1) = v(w_2)$.
\end{enumerate}
The implication (i)$\implies$(ii) follows from Lemma \ref{2.2}. Now assume (ii) holds. Let $v=v(w_1)\in \operatorname{Spv}_\text{d}^{(1)}(K_{w_1}K_{w_2})$. Then $k(v)$ is separably closed. We have $K_{w_1}K_{w_2}\subset K_v^\text{t}$ and hence $K_{w_1}K_{w_2}=K_v^\text{t}$ by Theorem \ref{theorem-absoluteinertia}. $\Gamma_v$ is equal to the value group of $v|_K\in\operatorname{Spv}_\text{d}^{(1)}(K)$, which is finitely generated. However, value groups of valuations on an algebraically closed field are divisible, hence $K_v^\text{t}$ can't be algebraically closed and neither can the composite $K_{w_1}K_{w_2}$.

@@

Let $n\in\mathbb{N}$. In this section we shall show that $\sigma: G_K\to G_{K'}$ induces group isomorphisms $\varphi_n: K'^\times/n\to K^\times/n$. By Proposition \ref{prop:kummer-theory}, we have isomorphisms:
\[ \mathrm{H}^1(K',\mu_n)\cong K'^\times/n,\qquad \mathrm{H}^1(K,\mu_n)\cong K^\times/n \]
Our goal is to establish an isomorphism between the corresponding cohomology groups.

>>>>

\begin{lemma}\label{2.2-pre}
Let $v,w\in\operatorname{Spv}(K)$. We have:
\[\mathcal{O}_w\subset\mathcal{O}_v \iff w\in\overline{\{v\}} \]
Thus $v$ is a closed point if and only if it has no non-trivial specializations. For a fixed $v\in \operatorname{Spv}(K)$ there is a canonical bijection: 
\begin{align*}
\{ w\in\operatorname{Spv}(K)\mid \mathcal{O}_w\subset\mathcal{O}_v \} &\longrightarrow \operatorname{Spv}k(v)\\ 
w&\longmapsto w\mod v
\end{align*}
Therefore, $v$ is a closed point if and only if $k(v)$ only admits the trivial valuation, i.e. $k(v)$ has characteristic $p>0$ and is algebraic over $\mathbb{F}_p$. In other words, if $|\operatorname{Spv}(K)|$ denotes the set of all closed points in $\operatorname{Spv}(K)$, we have:
\[ |\operatorname{Spv}(K)|=\{v\in\operatorname{Spv}(K)\mid \dim k(v)=0\} \]
If $w\in\operatorname{Spv}_\text{rd}^{(i)}(K)$ for some $i\geq 1$, then there exists a unique $v(w)\in\operatorname{Spv}_\text{rd}^{(i-1)}(K)$ such that $\mathcal{O}_w\subset\mathcal{O}_{v(w)}$. $w$ is henselian if and only if $v(w)$ and $w\mod v(w)$ are henselian.
\end{lemma}

@@

Let $A\subset \operatorname{Spv}(K)$ be a closed set, $S\subset K$ finite, and let $U_S\cap A\neq\varnothing$. Assume there exists a point $v\in U_S\cap A$ which is not closed. Let $\overline{S}$ be the image of $S\subset \mathcal{O}_v$ in $k(v)$. If $\operatorname{char}k(v)=0$, then $R=\mathbb{Z}[\overline{S}]\subset k(v)$ is a subring that is not a field since $\overline{S}$ is finite. If $\operatorname{char} k(v)=p>0$, $k(v)/\mathbb{F}_p$ is not an algebraic extension, thus we can find an element $T\in k(v)$ which is transcendental over $\mathbb{F}_p$. In this case, $R=\mathbb{F}_p[T, \overline{S}]\subset k(v)$ is a subring that is not a field. In both cases, \cite{ZS60} VI, §4 Corollary 1 to Lemma guarantees the existence of a non-trivial valuation $\widetilde{v_1}\in\operatorname{Spv}k(v)$ with $\overline{S}\subset R\subset \mathcal{O}_{\widetilde{v_1}}$. By Lemma \ref{2.2-pre}, $\widetilde{v_1}$ corresponds to a valuation $v_1\in\operatorname{Spv}(K)$ with $S\subset \mathcal{O}_{v_1}\subsetneq \mathcal{O}_v$, i.e. $v_1\in \overline{\{v\}}\cap U_S$ and $\operatorname{rank}(v_1)>\operatorname{rank}(v)$. Repeating this process for $v_1$ and so on, we get a specialization chain of valuations in $U_S$:
\[\mathcal{O}_v\supsetneq \mathcal{O}_{v_1}\supsetneq\cdots \supsetneq\mathcal{O}_{v_n} \]
Since $K$ is assumed to be finite dimensional, Lemma \ref{rank-dimension-inequality} assures that this sequence ends with a closed point $v_n\in \overline{\{v\}}\cap U_S\subset A\cap U_S$.

@@

\begin{proof}
Assume that $K$ is not algebraically closed. $w_1$ and $w_2$ can't be trivial, for otherwise $\dim k(w_i)=\dim (K)\neq 0$. By the Theorem of F.K. Schmidt \ref{theorem-fkschmidt}, we can see that $w_1,w_2$ are dependent. Since two different valuations of rank $1$ are independent, at least one of $w_1$ and $w_2$ is of rank $2$. Now assume that $w_1$ is, say, of rank $1$ and $w_2$ is of rank $2$. Since they are dependent, it follows $v(w_2) = w_1$ and $w_1$ has a non-trivial specialization, a contradiction to $w_1\in |\operatorname{Spv}(K)|$.

Thus $w_1,w_2$ are both of rank $2$ and by Lemma \ref{rank-dimension-inequality} we can see that $w_1,w_2\in\operatorname{Spv}_\text{rd}^{(2)}(K)$. Set $v_i=v(w_i)\in\operatorname{Spv}^{(1)}_\text{d}(K)$. By Lemma \ref{2.2-pre} $K$ is henselian with respect to both $v_1$ and $v_2$. Again, by the Theorem of F.K. Schmidt \ref{theorem-fkschmidt}, we get $v_1 = v_2$. Furthermore, $k(v_1) = k(v_2)$ is henselian with respect to two different valuations of rank $1$, namely $w_1\mod v_1$ and $w_2\mod v_1$, making $k(v_1)$ separably closed.

For the second assertion, let $K$ be not algebraically closed and $v=v(w_1)=v(w_2)\in\operatorname{Spv}_\text{d}^{(1)}(K)$. The restriction $v|$ of $v$ on $k=\mathbb{Q}(T)\subset K$ is a discrete valuation. Choose a henselization $k_{v|}$ of $k$ such that $k_{v|}\subset K$ and consider the absolute inertia field $k_{v|}^\text{t}$ of $k_{v|}$. Since $k(v)$ is separably closed, we have $k_{v|}^\text{t}\subset K$, i.e. $G_K\subset G_{k_{v|}^\text{t}}$. Since $v|\in \operatorname{Spv}_\text{d}^{(1)} ({k_{v|}^\text{t}})$ is discrete and henselian, \cite{Ka79} §5, Theorem 1 shows $\operatorname{cd}\big(G_{k_{v|}^\text{t}}\big)\leq 2$. In particular, $\operatorname{cd}(G_K)\leq 2$.
\end{proof}

@@

\begin{proof}
Let $T$ be the absolute inertia group of $K$ and $V\lhd T$ its absolute ramification group. By Theorem \ref{theorem-sylowgroups-inertiagroup}, $V$ is the $p$-Sylow group of $T$ and the $\ell$-Sylow group of $T/V$ is isomorphic to $\mathbb{Z}_\ell$. Therefore, by \cite{Se64} Ch. I, §3 Proposition 15:
\[ \operatorname{cd}_\ell(T)\leq \operatorname{cd}_\ell(V) + \operatorname{cd}_\ell(\mathbb{Z}_\ell) = 1 \]
By Theorem \ref{theorem-absoluteinertia}, we have an isomorphism $G_K/T\cong G_k$. Furthermore, we have $\operatorname{cd}_\ell(G_K/T)=\operatorname{cd}_\ell(k)\leq 2$ by requirement,
thus the following Hochschild-Serre spectral sequence degenerates on $E_2$:
\[E_2^{i,j}=\mathrm{H}^i(G_K/T, \mathrm{H}^j(T, \mathbb{Z}/\ell\mathbb{Z}(2)))\Longrightarrow\mathrm{H}^{i+j}(G_K, \mathbb{Z}/\ell\mathbb{Z}(2))\]
It yields an isomorphism $\mathrm{H}^2(k, \mathrm{H}^1(T, \mathbb{Z}/\ell\mathbb{Z}(2)))\cong \mathrm{H}^3(K, \mathbb{Z}/\ell\mathbb{Z}(2))$. Since $\mu_{\ell}$ is contained in the absolute inertia field of $K$, $T$ acts trivially on $\mu_{\ell}$, hence:
\[ \mathrm{H}^1(T, \mathbb{Z}/\ell\mathbb{Z}(2)) \cong \mathrm{H}^1(T, \mu_{\ell}) \cong \operatorname{Hom}_\text{cont.}(T, \mu_{\ell}) \cong \operatorname{Hom}_\text{cont.}(T/V, \mu_{\ell}) \]
By Theorem \ref{theorem-sylowgroups-inertiagroup}, $T/V$ is the free pro-$\mathcal{C}$ group of rank $1$ where $\mathcal{C}$ is the class of all finite groups with order prime to $p$. Therefore, $\operatorname{Hom}_\text{cont.}(T/V, \mu_{\ell})\cong \mu_{\ell}$. The rest follows from Proposition \ref{prop:kummer-theory}.
\end{proof}

The following lemma is the key result in proving Theorem \ref{thm:main-result}. First, we use K. Kato's two-dimensional local-global principle to show the assertion for finitely generated $K$. Then we'll use a quasi-compactness argument to drop the assumption that $K$ is finitely generated.

@@

\begin{proof}
Let $L=K(\mu_{\ell},\sqrt{-1})/K$. Consider the restriction and corestriction maps:
\[ \begin{tikzcd}
\mathrm{H}^3(K,\mathbb{Z}/\ell\mathbb{Z}) \ar[r, "\operatorname{res}"] & \mathrm{H}^3(L,\mathbb{Z}/\ell\mathbb{Z})\ar[r, "\operatorname{cor}"]& \mathrm{H}^3(K,\mathbb{Z}/\ell\mathbb{Z}) 
\end{tikzcd} \]
We have $\operatorname{cor}\circ\operatorname{res} = [L:K]$. Since $[L:K]$ is coprime to $\ell$, we see that $\operatorname{res}$ is injective. Thus we can assume that $K=L$, i.e. $\mu_{\ell}\subset K$ and $K$ is not formally real. Now we can replace $\mathbb{Z}/\ell\mathbb{Z}$ by $\mathbb{Z}/\ell\mathbb{Z}(2)$ and let us write $\mathrm{H}^3(L) = \mathrm{H}^3(L, \mathbb{Z}/\ell\mathbb{Z}(2))$.

@@

Let $v$ be a discrete valuation of $K$ with residue field $k=k(v)$. Consider the following map induced by the restriction maps: 
\[ \phi: \mathrm{H}^3(K_v) \longrightarrow \prod_w\mathrm{H}^3(K_w) \]
where $w$ ranges over all rank-$2$ valuations with $v(w) = v$. By Lemma \ref{rank-dimension-inequality}, we have $\dim(k) = 1$, thus $k$ is a global field of characteristic $0$, hence a number field. \cite{Se64} Ch. II, §4 Prop. 13 shows $\operatorname{cd}_\ell(k)\leq 2$. With Lemma \ref{2.4-pre}, $\phi$ can be identified with
\[ {}_\ell\operatorname{Br}(k) \longrightarrow \prod_{\widetilde{w}\in\operatorname{Spv}^{(1)}(k)} {}_\ell\operatorname{Br}(k_{\widetilde{w}}) \]
which is injective by the classical Hasse principle. Moreover, its image is contained in $\bigoplus {}_\ell\operatorname{Br}(k_{\widetilde{w}})$. Combining these maps yields the following injection:
\[\Phi: \mathrm{H}^3(K)\longrightarrow \bigoplus_{x\in\mathfrak{X}_1}\  \bigoplus_{\substack{w\in\operatorname{Spv}_\text{rd}^{(2)}(K) \\ v(w) = v_x}} \mathrm{H}^3(K_w) \]
The direct sum ranges over a subset of $|\operatorname{Spv}(K)|$, thus this concludes the proof. 
\end{proof}

@@

\begin{proof}
We adopt the notation from the previous proof. First, we shall prove that the following map is injective for every model $\mathfrak{X}$ of $K$:
\[ f: \mathrm{H}^3(K) \longrightarrow \prod_{y\in\mathfrak{X}_0}\mathrm{H}^3(K_y) \]
For $x\in\mathfrak{X}$ let $\mathcal{O}_x$ be a henselization of $\mathcal{O}_{\mathfrak{X}, x}$ and $K_x$ its quotient field. For $y\in\mathfrak{X}_0$ set $P_y=\operatorname{Spec}(\mathcal{O}_y)_1$. For $z\in P_y$ let $\mathcal{O}_z$ be a henselization of $\mathcal{O}_y$ at $z$ and $K_z$ its quotient field. For $y\in\mathfrak{X}_0$ and $x\in\mathfrak{X}_1$ let $P_{x,y}$ be the subset of $P_y$ consisting of all $z\in P_y$ which are mapped to $x$ under $\operatorname{Spec}(\mathcal{O}_y)\to\mathfrak{X}$. Consider the following commutative diagram:
\[ \begin{tikzcd}
\mathrm{H}^3(K)\ar[r, "\varphi"]\ar[d, "f"'] & \displaystyle\prod_{x\in\mathfrak{X}_1}\mathrm{H}^3(K_x)\ar[d, "\psi"]\\
\displaystyle\prod_{y\in\mathfrak{X}_0}\mathrm{H}^3(K_y) \ar[r, "g"']& \displaystyle\prod_{\substack{x\in\mathfrak{X}_1 \\ y\in\mathfrak{X}_0}}\prod_{z\in P_{x,y}}\mathrm{H}^3(K_z)
\end{tikzcd} \]
According to \cite{Sa87} Theorem 5.3, $g$ is injective. Now $\psi\circ\varphi$ can be identified with the injective map $\Phi$ from the proof of the previous Lemma. Thus its image is contained in $\bigoplus\mathrm{H}^3(K_w)$. Therefore, $f$ is injective as well and its image is contained in $\bigoplus\mathrm{H}^3(K_y)$. This shows that the set
\[ A_\mathfrak{X} = \{ y\in\mathfrak{X}_0\mid \operatorname{res}_{K_y/K}(\alpha)\neq 0 \} \]
is finite, thus closed in $\mathfrak{X}$. Now Lemma \ref{2.3} (i) yields
\[ \operatorname{supp}(\alpha) = \bigcap_{\mathfrak{X}\in \mathfrak{M}(K)} \pi_\mathfrak{X}^{-1}(A_\mathfrak{X}) \]
and the right-hand side is closed in $\operatorname{Spv}(K)$.
\end{proof}

@@

Let $w\in |\operatorname{Spv}(K)|$. We denote the restriction of $w$ to $K_i$ with $w$ as well. Since $\mathrm{H}^3(K_w) = \varinjlim_I \mathrm{H}^3((K_i)_w)$, there exists an $i = i(w)\in I$ such that $\operatorname{res}_{(K_i)_w/K}(g) = 0$. By Lemma \ref{2.4-closedset}, there is an open neighborhood $U_{i(w)}\subset |\operatorname{Spv}(K_i)|$ of $w$ such that $\operatorname{res}_{(K_i)_v/K}(g)=0$ for all $v\in U_{i(w)}$. For $K_i\subset K_j\subset K$ let
\[ \varphi_i: |\operatorname{Spv}(K)| \to |\operatorname{Spv}(K_i)| \]
\[ \varphi_{ij}: |\operatorname{Spv}(K_j)|\to |\operatorname{Spv}(K_i)| \]
be the restriction maps. They are continuous. Since $|\operatorname{Spv}(K)|$ is quasi-compact by Lemma \ref{spv-topology}, we can find a finite set $S\subset |\operatorname{Spv}(K)|$ such that:
\[ \bigcup_{w\in S}\varphi^{-1}_{i(w)}(U_{i(w)}) = |\operatorname{Spv}(K)| \]
Let $j\in I$ such that $K_j$ is the composite of the fields $K_{i(w)},\ w\in S$. Then we have:
\[ \bigcup_{w\in S}\varphi^{-1}_{i(w)j}(U_{i(w)}) = |\operatorname{Spv}(K_j)| \]
Let $v\in |\operatorname{Spv}(K_j)|$ and let $i = i(w),\ w\in S$ such that $v\in\varphi_{ij}^{-1}(U_{i(w)})$. We have:
\[ \operatorname{res}_{(K_j)_v/K_j}(\operatorname{res}_{K_j/K_0}(\beta)) = \operatorname{res}_{(K_j)_v/(K_i)_v}(\operatorname{res}_{(K_i)_v/K_0}(\beta)) = 0 \]
Since $K_j$ is finitely generated we obtain $\operatorname{res}_{K_j/K_0}(\beta) = 0$ with Lemma \ref{2.4-finitelygenerated}, thus $\alpha = \operatorname{res}_{K/K_0}(\beta) = 0$.
\end{proof}

@@

By Proposition \ref{2.5}, $E_0/E$, and also $E'_0/E'$, satisfy the condition of Proposition \ref{2.6} for both $\ell_1$ and $\ell_2$. Thus there exists a unique henselian valuation $w'_{E'}\in|\operatorname{Spv}(E')|$. Now $E'$ contains a henselization $K'_{w'}$ with respect to $w' = w'_{E'}|_{K'}$. By applying the same argument to $\sigma^{-1}$ we see that $E' = K'_{w'}$.

@@

Let $w_1,w_2 \in\operatorname{Spv}_\text{d}^{(2)}(K)$ be two different valuations. Then the following statements are equivalent:
\begin{enumerate}[(i)]
\item The composite $K_{w_1}K_{w_2}$ is not algebraically closed.
\item $w_1,w_2\in\operatorname{Spv}_\text{rd}^{(2)}(K)$ and $v(w_1) = v(w_2)$.
\end{enumerate}
The implication (i)$\implies$(ii) follows from Lemma \ref{2.2}. Now assume (ii) holds. Let $v=v(w_1)\in \operatorname{Spv}_\text{d}^{(1)}(K_{w_1}K_{w_2})$. Then $k(v)$ is separably closed. We have $K_{w_1}K_{w_2}\subset K_v^\text{t}$ and hence $K_{w_1}K_{w_2}=K_v^\text{t}$ by Theorem \ref{theorem-absoluteinertia}. $\Gamma_v$ is equal to the value group of $v|_K\in\operatorname{Spv}_\text{d}^{(1)}(K)$, which is finitely generated. However, value groups of valuations on an algebraically closed field are divisible and in particular not finitely generated, hence $K_v^\text{t}$ can't be algebraically closed and neither can the composite $K_{w_1}K_{w_2}$.

@@

Let $n\in\mathbb{N}$. In this section we shall show that $\sigma: G_K\to G_{K'}$ induces group isomorphisms $\varphi_n: K'^\times/n\to K^\times/n$. By Proposition \ref{prop:kummer-theory}, we have isomorphisms:
\[ \mathrm{H}^1(K',\mu_n)\cong K'^\times/n,\qquad \mathrm{H}^1(K,\mu_n)\cong K^\times/n \]
In this section, our goal is to establish an isomorphism between the corresponding cohomology groups.
